---
title: "optimal_partition_report figures"
author: "Nelson Jaimes"
date: "7/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_data, include = FALSE, echo = FALSE}
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(forcats)
library(cowplot)
library(purrr)
library(tibble)
library(wesanderson)
library(knitr)
library(plotly)

setwd("~/from_github/Project4")



```

## Plots


```{r Figure1, echo=FALSE}
raw_data <- read.csv(file = "output_2021-07-03.csv", header = TRUE)
plot_ly(raw_data, x=~length, y = ~number_of_partitions, z = ~executions, type="scatter3d", mode="markers",color = ~length)
```
Figure 1. This plot shows how the number of executions decreases as the number of partitions decrease, with a greater effect as the difference between array length and number of partitions becomes larger. This data uses delay tolerance. It appears to have greater variability than without delay tolerance.

```{r Figure2, echo=FALSE}
raw_data_not_delay_tolerant <- read.csv(file = "output_2021-07-03_not_delay_tolerant.csv", header = TRUE)
plot_ly(raw_data_not_delay_tolerant, x=~length, y = ~number_of_partitions, z = ~executions, type="scatter3d", mode="markers",color = ~length)
```
Figure 2. This plot shows how the number of executions decreases as the number of partitions decrease, with a greater effect as the difference between array length and number of partitions becomes larger. This is data without delay tolerance. It appears to have less variability than with delay tolerance.